Extended Data

### 2022-02-20 doc/manuscript/Dow_manuscript_Nature.Rmd
edit FIg. 2 caption
added explanation of DOY variables

![**Figure 2 | Foliage (a,b) and stem growth (c,d) phenology at the Smithsonian Conservation Biology Institute (a,c) and Harvard Forest (b,d).** Panels (a-b) show ecosystem-level canopy foliage phenology from 2001-2018, obtained from the MODIS Global Vegetation Phenology product (MCD12Q2.006), where G = Greenup, M=Mid-greenup, P=peak, and S=Senescence (i.e., beginning of green-down). Canopy foliage variables were extracted from a single pixel at the center of each forest plot. Only data flagged as "good" or "best" quality were included in the calculation of these phenology variables. Panels (c-d) show the dates at which stem growth milestones were achieved, on average, for sampled populations of ring-porous and diffuse-porous trees at SCBI (2011-2020) and Harvard Forest (1998-2003). Mean temperature was calculated for each xylem architecture/site combination over the respective critical $T_{max}$ window, then turned into a ratio and assigned a color on a gradient where the coldest year in the sample is blue and the warmest is red. Leaf phenology years are colored according to temperature in the critical $T_{max}$ window which had the best correlation with timing of greenup (ring-porous window at HF and diffuse-porous at SCBI).](tables_figures/DOYtiming_allyears.png){ width=25% }

>>>>

![**Figure 2 | Foliage (a,b) and stem growth (c,d) phenology at the Smithsonian Conservation Biology Institute (a,c) and Harvard Forest (b,d).** Panels (a-b) show ecosystem-level canopy foliage phenology from 2001-2018, obtained from the MODIS Global Vegetation Phenology product (MCD12Q2.006) for a single pixel at the center of each forest plot, where G = Greenup, M=Mid-greenup, P=peak, and S=Senescence (i.e., beginning of green-down). Panels (c-d) show the dates at which stem growth milestones were achieved, on average, for sampled populations of ring-porous and diffuse-porous trees at SCBI (2011-2020) and Harvard Forest (1998-2003). Mean $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ were estimated using the Bayesian model visualized, with confidence intervals, in `r EDF_pheno_Tmax_climwin`. Mean temperature was calculated for each xylem architecture/site combination over the respective critical $T_{max}$ window, then turned into a ratio and assigned a color on a gradient where the coldest year in the sample is blue and the warmest is red. Leaf phenology years are colored according to temperature in the critical $T_{max}$ window which had the best correlation with timing of greenup (ring-porous window at HF and diffuse-porous at SCBI).](tables_figures/DOYtiming_allyears.png){ width=25% }
